---
output: pdf_document
---

## Section 12. Reference Guide

### Section 12.1. Equation Reference {#equation-section}


\begin{equation}
  \label{eq:asd}
  x_{t}=t_{t}*s_{t}*c_{t}*e_{t}
\end{equation}

\begin{equation}
  x_{t}=t_{t}+s_{t}+c_{t}+e_{t}
\end{equation}

\begin{equation}
  E[x_{t}]=\mu
\end{equation}

\begin{equation}
  \label{eq:asdf}
  Var(x_{t})=\sigma_{x}^{2}
\end{equation}

\begin{equation}
  \label{eq:asdfg}
  Cov(x_{t}, x_{t-k}=R(k))
\end{equation}

#### Section 12.1.1. Ref to Equation

If we want to refer to an equation we need to implement the command

-   `\ref{eq:asd}`

Here we refer to equation \ref{eq:asd} or to equation \ref{eq:asdfg}.

### Section 12.2. Section Reference

Here I refer to another section [12.1](#equation-section).

### Section 12.3. Plot Reference

First we create a plot:

You can also embed plots, for example:

```{r histir, echo=TRUE, fig.cap="Captionerino Uno"}
hist(iris[[2]], main="HELLOO kjsahdlhsjkd")
```

Here I refer to Figure \ref{fig:histir}.

### Section 12.4. Table Reference

```{r carserino, echo=TRUE}
knitr::kable(mtcars[1:5, 1:5], caption="The mtcars data.", format="latex")
```

Here I refer to the Table \ref{tab:carserino}

### Section 12.5. Bibliography Reference

In order to use bibliography reference, we need to add a specific `.bib`-file in which add the literature we use for this paper.

The objects in the `.bib`-file have to be formated correctly:

    @inbook{source1,
        author = "Philipp Rieser",
        title = {The Book of Phil},
        year = "2019",
        publisher = "ZHAW", 
        address="Winterthur",
        pages = {113}
    }

    @online{source2,
        author="Pascal Bühler",
        title="Webpage of the Rings",
        url="www.webpagerino-of-the-rings.org",
        year="2020",
        note={[Stand: 19.09.2020]}
    }

No we can refer to each of these `.bib`-objects. You can use `[@source1]` to refer at the first source.

E.g.: Philipp Rieser says in this book dbl a hd hdj dhasd hda sdahjk dhsd [@source1, pp. 33-35]

Source Reference [@source2]. Or we refer to the third source [@source3]

Markdown/LaTeX will create automatically a list of the used `.bib`-objects at the end of the file, which can be used as the Reference List at the end of the paper.
